### 2019-10-11 thesis/txt/2-models.tex
small fixes in devmail and make thesis compile

>>>>

\plan{a build consists of various steps, executed by different tools, these are often orchestrated by at least one overarching tool. // picture: overarching tool travis and it calls different tools which tehn output sequentiall, travis sometimes outputs something in between -> that is how the build log is made up // we have this structure though it is not always apparent from the build log / edges between the systems can look very different, mostly no agreed model, we: look at differen techniques to extract certain pieces of information \emph{without complete parsing the whole log in to a structure} -> we don't necesarrily want to understand the whole log sturcture just extract one specifi information relevant to us}
